Correlation between photons emitted in diferent channels from an atom inside a leaky driven cavity

### 2019-12-19 newpaper.tex
Agregrue agradecimientos
Segunda quase version final

\title{Correlation between different emission channels from an atom inside a leaky driven cavity}% Force line breaks with \\

\author{Guillermo Preisser}
 \email{Corresponding author e-mail: guillermo.preisser@uabc.edu.mx}
 %Lines break automatically or can be forced with \\
\author{Pablo Barberis}%
\affiliation{Instituto de Investigaciones en Matemáticas Aplicadas y en Sistemas, Universidad Nacional Autónoma de México, Ciudad Universitaria, 04510, CDMX, México.}

@@

\begin{abstract}
A two level atom in free space does not show any correlation between
  photons emitted in different directions. We consider a two level
  atom inside a driven leaky cavity. We consider two atomic emission
  channels: emission to cavity modes and emission to no-cavity modes.
  Using the quantum trajectory formalism we study the correlation
  between photons emitted into cavity modes and that leak the cavity
  through its mirror, with photons that are emitted into the rest of
  the modes. We find that the cavity generates a correlation between
  the two emission channels.
\end{abstract}

@@

Spontaneous emission is a phenomenon that has been studied since the
early XX century \cite{10.2307/94746, 1917PhyZ...18..121E}. One of the
main characteristics of spontaneous emission is that the exact time of
emission, as well as the direction in which the photon is emitted, is
random, which difficults its measurement. On the other hand, photons
emitted from a cavity mirror are easier to measure because we know
their direction \cite{326305, doi:10.1063/1.113345}. The randomness of
the direction in which the photons are emitted by atoms in free space
difficults photon counting experiments. To sort out this difficulty
one could think of a physical arrangement in which a two-level atom is
coupled to a driven cavity, as it is shown in Fig. \ref{asa}. In this
physical arrangement, one could try to estimate the number of
spontaneous emissions of the atom --photons that are emitted in modes
that are not cavity modes and therefore escape the cavity to its
side-- by measuring the cavity emissions --photons that leak through
one of the cavity mirrors. In the case that a correlation exists
between the two quantities, we can count the number of photons that
leak the cavity through its mirror, which is easy to measure, to find
information about the number of photons emitted into the other modes
(spontaneous emission), which are difficult to measure.

In the case of a two-level atom in free space, the absence of
correlation between photons emitted in different directions is due to
the fact that the atom's environment memory of previous interactions
with it, is very short; this is what justify the markovian
approximation \cite{daley2014quantum}. Two atomic emissions would be
correlated if one of the emissions stay registered in the environment
and, somehow, influence the second emission.

For an atom in free space, knowing the number of photons emitted in
some region of the space during some time does not give any
information on the number of photons emitted in other region of the
space. Nevertheless, for the case of an atom inside a cavity, before a
photon, emitted from the atom into the cavity mode, leaks the cavity,
it will interact with the atom for some time. This interaction could
create a correlation between photons that leak the cavity through its
mirror and photons that are emitted from the atom to the cavity side
(spontaneous emissions).

@@

This article is organized as follows: A general overview of the
theoretical model is presented in section \ref{sc:drivenjc}. In
section \ref{sc:distributions} we obtain the joint probability
distribution of the  number of spontaneous and cavity emissions. In
section \ref{sc:correlation} we calculate the correlation between the
two variables. Concluding remarks are given in section
\ref{sc:conclusions}
\begin{center}
\begin{figure*}\label{asa}
\begin{center}
\includegraphics[scale = 0.65]{newimagepaper.pdf}
%\includegraphics[scale = 0.45]{image_paper222.png}
\caption{A driven atom in free space (a) and inside a driven leaky
  cavity (b). We count the number of photons $m$ and $n$, emitted by
  the atom in two different directions. For the atom in free space
  there is no correlation between $m$ and $n$. For the atom inside the
  leaky cavity we find a correlation between $m$ and $n$.}
\end{center}
\end{figure*}
\end{center}

\section{Theoretical model}\label{sc:drivenjc}
We consider a system consisting of a two-level atom, coupled to a mode
of a leaky cavity. The mode is driven by a coherent field resonant
with the atomic transition and the cavity mode.
% In order to account for
% dissipation one may use a non-hermitian Hamiltonian to describe the
% system \cite{bla}. Using this description for the system will turn
% useful at the moment of using quantum trajectory theory. Such
% Hamiltonian can be separated into hermitian and non-hermitian terms.
%\begin{equation}
%H = H_s - \frac{i\hbar}{2}\sum_m C^\dagger_n C_n .
%\end{equation}
The Hamiltonian of this system, in the rotating wave approximation is
given by
\begin{equation}
H_s = H_{at} + H_{cav} + H_{atcav} + H_{lascav}, \label{mainham}  
\end{equation}
where the atom and cavity terms are, respectively
\begin{subequations}
\begin{equation}
H_{at} = \tfrac{1}{2}\hbar \omega \sigma_z,    
\end{equation}
\begin{equation}
H_{cav} = \hbar \omega  a^\dagger a,  
\end{equation}
while the coupling between atom and cavity, and cavity and coherent
field are
\begin{equation}
H_{atcav} = i\hbar g(a\sigma_+ - a^\dagger \sigma_-),    
\end{equation}
\begin{equation}
H_{lascav} = i\hbar \mathcal{E}(ae^{i\omega t} - a^\dagger e^{-i\omega t}),    
\end{equation}
\end{subequations}
where the annihilation operator $a$ of a single photon in the cavity,
and the creation operator $a^\dagger$ obey $[a, a^\dagger] = 1$. The
operators $\sigma_-, \sigma_+$ account for the atomic lowering and
raising operators, respectively, and the operator $\sigma_z$ accounts
for the population difference between the atomic levels. These
operators obey
$[\sigma_+, \sigma_-] = \sigma_z, \ [\sigma_\pm, \sigma_z] = \mp
2\sigma_\pm$. The strength of the coupling between atom and cavity
field is given by the constant
\begin{equation}
g = \sqrt{\frac{\omega d^2}{2\hbar \epsilon_0 V_Q}},
\end{equation}
where $V_Q$ is the mode volume, $d$ is the atomic dipole, and
$\epsilon_0$ is the permittivity of free space. $\mathcal{E}$ is a term
proportional to the coherent field amplitude. Dissipation is
introduced by the following non-hermitian Hamiltonian
\begin{equation} \label{nh}
H_{nh} = H_{dec} + H_{leak},
\end{equation}
where the terms corresponding to spontaneous emission of the atom and cavity losses are
\begin{subequations}
\begin{equation}
H_{dec} = - i\hbar\frac{\gamma}{2}\sigma_+\sigma_-,
\end{equation}
\begin{equation}
H_{leak} = - i\hbar\kappa a^\dagger a\, ,
\end{equation}
\end{subequations}
where $\kappa$ and $\gamma$ are the cavity loss and spontaneous decay
rate. The evolution between jumps is given by $H=H_s+H_{nh}$. This
evolution is interrupted by spontaneous emission by the atom or when a
photon leaks the cavity.

We now summarize the quantum trajectory formalism \cite{bla} that we
use to solve the system. Each quantum trajectory is simulated as
follows. We start with a state which represents a ground state of the
atom with no photons in the cavity,
$\ket{\phi(t = 0)} = \ket{\downarrow} \times \ket{0}$, we evolve it
with the Schrödinger equation through some time $\delta t$, using the
non-hermitian Hamiltonian
\begin{equation}
H = H_s +H_{nh}\, .
\end{equation}
The evolution of the state through the Schrodinger equation will be
interrupted by a quantum jump – an abrupt change on our state in which
a photoemission has occurred. The probability for such quantum jump to
happen, during the time step $\delta t$, is given by the collapse
probability
\begin{equation} \label{probcol}
\delta p = \sum_n \delta p_n,
\end{equation}
where

@@

\ENDIF
\ELSE
\STATE $\ket{ \phi(t + \delta t)} = \frac{\ket{\phi^1 (t+ \delta t)}}{\sqrt{1-\delta p}}$
\STATE $t \ += \delta t$
\ENDIF
\ENDFOR
\RETURN  $N_{CA}$
\end{algorithmic}
\end{algorithm}
We compare the collapse probability of Eq.~\eqref{probcol} with a
random number $\epsilon$, uniformly distributed between zero and one.
In the case the condition $\delta p > \epsilon$ is fulfilled we
simulate that a quantum jump has happened, by acting with one of the
collapse operators $a$ or $\sigma_-$ and renormalizating the obtained
state. The operator that will act on the state will be given according
to the relative probabilities of Eqs.~\eqref{relprob}.
\begin{figure}[!t] 
\centering
\includegraphics[scale = 0.5]{distributioneng.pdf}
\caption{Probability distribution of spontaneous emissions for
  different number of cavity photons. Parameters $\mathcal{E}  =
  \kappa =  g = 1\gamma$, $100,000$ quantum trajectories. } \label{probdiss}
\end{figure}
If $\delta p > \epsilon$ is not fulfilled we just renormalize the
state, because using a non-hermitian Hamiltonian will have as a
consequence that the probability won't be conserved
\cite{Sakurai:1167961}. For the next step we repeat the procedure
using the resulting state for this step. One quantum trajectory of
total time $t$ is obtained after repeating the previous procedure
$t/\delta t$ steps. For each trajectory we count the number of quantum
jumps, the jumps corresponding to operator $a$ reduces the number of
photons inside the cavity and corresponds to a photon that leak the
cavity. The jumps corresponding to operator $\sigma_-$ interrumps its
unitary evolution and send it back to the ground state, it corresponds
to a spontaneous emission. The procedure to register emissions in the
two different channels is summarized in algorithm. \ref{alg1}.

We realize a large number of these trajectories and keep track of the
numbers of emission for each channel, with this data we can calculate
probability distributions that relate these two quantities.

@@

\begin{equation} \label{chaf1}
\expval{a}_{ss} = \frac{\mathcal{E}e^{-i\omega t} +
  g\expval{\sigma_-}_{ss}}{\kappa}\, ,
\end{equation}
\begin{equation} \label{chaf2}
\expval{\sigma_-}_{ss} = -\frac{2g}{\gamma}\frac{\expval{a}_{ss}}{1 +
  \frac{8g^2}{\gamma^2}|\expval{a}_{ss}|^2}\, ,
\end{equation}
\begin{equation}
\bigg(\frac{\mathcal{E}}{\kappa}\bigg)^2 = |\expval{a}_{ss}|^2 \bigg(1
+ \frac{2g^2}{\gamma \kappa}\frac{1}{1 +
  \frac{8g^2}{\gamma^2}|\expval{a}_{ss}|^2}\bigg)^2\, .
\end{equation}
When $\gamma \gg g$, the expected value of the number of photons in
the cavity is 
\begin{equation} \label{numfo}
|\expval{a}_{ss}|^2 \approx \bigg(\frac{\mathcal{E}/\kappa}{1 + 2g^2/\gamma \kappa}\bigg)^2.
\end{equation}

\subsection{Quantum trajectories with fixed number of photons leaked from the cavity}
We calculate the distribution probability of the number of spontaneous
emission when a fixed number of photons leaked the cavity. We assume
that the mean number of photons inside the cavity is $1/9$. The
results are shown in Fig.~\ref{probdiss}. As the number of cavity
emissions increases, the mean number of spontaneous emissions
increases. This result is expected, because the number of cavity
emissions is correlated with the time we are counting spontaneous
emission photons from the atom: the larger the number of cavity
emissions the larger the time we count spontaneous emitted photons,
which implies a larger mean number of emitted photons. Also, as shown
in Fig~\ref{graph}, the probability distribution is wider as the
number of leaked photons increases, this implies less accuracy
guessing the number of spontaneous emission. If we know the cavity
drive, this results does not imply that we can learn something extra
about the number of spontaneous emissions knowing the number of
photons leaked from the cavity; it is clear that when we increase the
time window where we count photons, both, the number of cavity emissions
and the number of spontaneous emissions, increases.

@@

\subsection{Quantum trajectories with fixed duration}
We consider the set of quantum trajectories of the same duration. This
corresponds to fixing the time we count photons. Each set of quantum
trajectories with the same duration is labeled with its mean number
of spontaneous emitted photons $\langle n_s\rangle$, given the system
parameters, a larger $\langle n_s\rangle$ implies quantum trajectories
with larger duration. We consider the case where we fix the mean
number of photons inside the cavity to $1$. As shown by
Eq.~(\ref{numfo}), this number depends on the drive, and cavity and
atomic parameters.

@@

Now we focus in the case, where given a set of quantum trajectories
with fixed duration, we postselect all the trajectories where the
number of cavity emissions is a fixed number $n_c$, and plot
$p(n_s|n_c)$, the probability distribution of the number of spontaneous
emissions $n_s$, under the condition that $n_c$ cavity emissions
happened. If $p(n_s|n_c)\neq p(n_s)p(n_c)$, $n_s$ and $n_c$ are not
independent: information can be extracted about $n_s$ knowing $n_c$.
An example of this is shown in Fig.~\ref{probdisult}(a), where we
show $p(n_s|n_c)$, the probability distribution of $n_s$ postselected
to the case where the number of cavity emissions is
$n_c=\langle n_c \rangle$, and $n_c=\langle n_c \rangle\pm\sigma$. We
see a positive correlation between the two random variables: the
maximum of the probability distribution increases (decreases) if we
postselect the trajectories with a larger than the mean (smaller than
the mean) number of cavity emissions. In Fig.~\ref{probdisult}(b), we
show that for a cavity with large $\kappa$, the change in the
probability distribution $p(n_s|n_c)$ is much smaller than in the case
for small $\kappa$. When
$\kappa\rightarrow\infty$, there are no correlation between the two
channels and $p(n_s|n_c)=p(n_s)p(n_c)$.
In the next section we calculate the correlation between $n_s$ and
$n_c$ for different $\kappa$.

@@

The results are shown in Fig. \ref{corrxy}. We see a maximum
correlation close to $0.1$ for $\kappa/\gamma\approx 0.05$ that
decreases as $\kappa$ increases. The figure is consistent with the
statement that the correlation goes to zero as
$\kappa\rightarrow\infty$. With values for $\kappa/\gamma$ lower than
$0.05$, we notice that the correlations begins to decrease. The reason
is that, as the cavity linewidth decreases, the number of cavity
emissions decreases. In the limit where $\kappa=0$ the two random
variables becomes independent, because the output of $n_c$ is zero
with probability one. In this case there is no correlation between the
two random variables. Fig.~\ref{probdisult}(a), where the change in
$p(n_s|n_c)$ is larger, corresponds to a correlation around $0.1$;
Fig.~\ref{probdisult}(b), where the change is small, corresponds to a
correlation around $0.01$.

@@

>>>>

\title{Correlation between photons emitted in diferent channels from
  an atom inside a leaky driven cavity}% Force line breaks with \\

\author{Guillermo Preisser}
 \email{Corresponding author e-mail: guillermo.preisser@uabc.edu.mx}
 %Lines break automatically or can be forced with \\
\author{Pablo Barberis-Blostein}%
\affiliation{Instituto de Investigaciones en Matemáticas Aplicadas y en Sistemas, Universidad Nacional Autónoma de México, Ciudad Universitaria, 04510, CDMX, México.}

@@

\begin{abstract}
  Photons emitted by a driven two level atom in free space do not show
  correlation between different directions. We consider a two level
  atom inside a driven leaky cavity. We consider two atomic emission
  channels: emission to cavity modes and emission to no-cavity modes.
  Using the quantum trajectory formalism we study the correlation
  between photons emitted into cavity modes and that leak the cavity
  through its mirror, with photons that are emitted into the other
  modes. We find that the cavity generates a correlation between the
  two emission channels.
\end{abstract}

@@

Spontaneous emission has been studied since the early XX century
\cite{10.2307/94746, 1917PhyZ...18..121E}. One its main
characteristics is that the exact time of emission, as well as the
direction in which the photon is emitted, is random, which difficults
its measurement. On the other hand, photons that leak a cavity mirror
are easier to measure because we know their direction \cite{326305,
  doi:10.1063/1.113345}. The randomness of the direction in which the
photons are emitted by atoms in free space difficults photon counting
experiments. To sort out this difficulty one could think of a physical
arrangement in which a two-level atom is coupled to a driven cavity,
as it is shown in Fig. \ref{asa}. In this physical arrangement, we
have two emission channels: spontaneous emissions of the atom
--photons that are emitted in modes that are not cavity modes and
therefore escape the cavity to its side-- and cavity emissions
--photons that leak through one of the cavity mirrors. In the case
that a correlation exists between the two channels, we can count the
number of photons that leak the cavity through its mirror, which is
easy to measure, to find information about the number of photons
emitted into the other modes (spontaneous emission), which are
difficult to measure.

In the case of a two-level atom in free space, the absence of
correlation between photons emitted in different directions is due to
the fact that the atom's environment memory of previous interactions
with it, is very short; this is what justifies the markovian
approximation \cite{daley2014quantum}. Two atomic emissions would be
correlated if one of the emissions stay registered in the environment
and, somehow, influence the second emission.

For an atom inside a cavity, before a photon, emitted from the atom
into the cavity mode, leaks the cavity, it will interact with the atom
for some time. This interaction could create a correlation between
photons that leak the cavity through its mirror and photons that are
emitted from the atom to the cavity side (spontaneous emissions).

@@

This article is organized as follows: A general overview of the
theoretical model is presented in section \ref{sc:drivenjc}. In
section \ref{sc:distributions} we obtain the joint probability
distribution of the  number of spontaneous and cavity emissions. In
section \ref{sc:correlation} we calculate the correlation between the
two variables. Concluding remarks are given in section
\ref{sc:conclusions}
\begin{center}
\begin{figure*}
\includegraphics[scale = 0.65]{newimagepaper.pdf}
\caption{A driven atom in free space (a) and inside a driven leaky
  cavity (b). We count the number of photons $m$ and $n$, emitted by
  the atom in two different directions. For the atom in free space
  there is no correlation between $m$ and $n$. For the atom inside the
  leaky cavity we find a correlation between $m$ and $n$.}\label{asa}
\end{figure*}
\end{center}

\section{Theoretical model}\label{sc:drivenjc}
We consider a system consisting of a two-level atom, coupled to a mode
of a leaky cavity. The mode is driven by a coherent field resonant
with the atomic transition and the cavity mode.
% In order to account for
% dissipation one may use a non-hermitian Hamiltonian to describe the
% system \cite{bla}. Using this description for the system will turn
% useful at the moment of using quantum trajectory theory. Such
% Hamiltonian can be separated into hermitian and non-hermitian terms.
%\begin{equation}
%H = H_s - \frac{i\hbar}{2}\sum_m C^\dagger_n C_n .
%\end{equation}
The Hamiltonian of this system, in the rotating wave approximation, is
given by
\begin{equation}
H_s = H_{at} + H_{cav} + H_{atcav} + H_{lascav}, \label{mainham}  
\end{equation}
where the atom and cavity terms are, respectively
\begin{subequations}
\begin{equation}
H_{at} = \tfrac{1}{2}\hbar \omega \sigma_z,    
\end{equation}
\begin{equation}
H_{cav} = \hbar \omega  a^\dagger a,  
\end{equation}
$\omega$ is the cavity mode frequency and the atomic transition
frequency. The atom is in resonance with the cavity mode. 
The coupling between atom and cavity, and cavity and coherent
field are
\begin{equation}
H_{atcav} = i\hbar g(a\sigma_+ - a^\dagger \sigma_-),    
\end{equation}
\begin{equation}
H_{lascav} = i\hbar \mathcal{E}(ae^{i\omega t} - a^\dagger e^{-i\omega t}),    
\end{equation}
\end{subequations}
where the annihilation operator $a$ of a single photon in the cavity,
and the creation operator $a^\dagger$ obey $[a, a^\dagger] = 1$. The
operators $\sigma_-, \sigma_+$ account for the atomic lowering and
raising operators, respectively, and the operator $\sigma_z$ accounts
for the population difference between the atomic levels. These
operators obey
$[\sigma_+, \sigma_-] = \sigma_z, \ [\sigma_\pm, \sigma_z] = \mp
2\sigma_\pm$. The strength of the coupling between atom and cavity
field is given by the constant
\begin{equation}
g = \sqrt{\frac{\omega d^2}{2\hbar \epsilon_0 V_Q}},
\end{equation}
where $V_Q$ is the mode volume, $d$ is the atomic dipole, and
$\epsilon_0$ is the permittivity of free space. $\mathcal{E}$ is a
term proportional to the coherent field that drives the cavity in
resonance. Dissipation is introduced by the following non-hermitian
Hamiltonian
\begin{equation} \label{nh}
H_{nh} = H_{dec} + H_{leak},
\end{equation}
where the terms corresponding to spontaneous emission of the atom and cavity losses are
\begin{subequations}
\begin{equation}
H_{dec} = - i\hbar\frac{\gamma}{2}\sigma_+\sigma_-,
\end{equation}
\begin{equation}
H_{leak} = - i\hbar\kappa a^\dagger a\, ,
\end{equation}
\end{subequations}
where $\kappa$ and $\gamma$ are the cavity loss and spontaneous decay
rate. The evolution between jumps is given by $H=H_s+H_{nh}$. This
evolution is interrupted by spontaneous emission by the atom or when a
photon leaks the cavity.

We now summarize the quantum trajectory formalism \cite{bla} that we
use to solve the system. Each quantum trajectory is simulated as
follows. We start with a state which represents a ground state of the
atom with no photons in the cavity,
$\ket{\phi(t = 0)} = \ket{\downarrow} \times \ket{0}$, we evolve it
with the Schr\"odinger equation through some time $\delta t$, using the
non-hermitian Hamiltonian
\begin{equation}
H = H_s +H_{nh}\, .
\end{equation}
The evolution of the state through the Schrodinger equation will be
interrupted by a quantum jump – an abrupt change on our state in which
a photoemission has occurred. The probability for such quantum jump to
happen, during the time step $\delta t$, is given by the collapse
probability
\begin{equation} \label{probcol}
\delta p = \sum_n \delta p_n,
\end{equation}
where

@@

\ENDIF
\ELSE
\STATE $\ket{ \phi(t + \delta t)} = \frac{\ket{\phi^1 (t+ \delta t)}}{\sqrt{1-\delta p}}$
\STATE $t \ += \delta t$
\ENDIF
\ENDFOR
\RETURN  $N_{CA}$
\end{algorithmic}
\end{algorithm}
We compare the collapse probability of Eq.~\eqref{probcol} with a
random number $\epsilon$, uniformly distributed between zero and one.
In the case the condition $\delta p > \epsilon$ is fulfilled we
simulate that a quantum jump has happened, by acting with one of the
collapse operators $a$ or $\sigma_-$ and renormalizating the obtained
state. The operator that will act on the state will be given according
to the relative probabilities of Eqs.~\eqref{relprob}.
\begin{figure}[!t] 
\centering
\includegraphics[scale = 0.5]{distributioneng.pdf}
\caption{Probability distribution of spontaneous emissions for
  different number of cavity photons. Parameters $\mathcal{E}  =
  \kappa =  g = 1\gamma$, $100,000$ quantum trajectories. } \label{probdiss}
\end{figure}
If $\delta p > \epsilon$ is not fulfilled we just renormalize the
state, because using a non-hermitian Hamiltonian will have as a
consequence that the probability won't be conserved
\cite{Sakurai:1167961}. For the next step we repeat the procedure
using the new state. One quantum trajectory of total time $t_f$ is
obtained after repeating the previous procedure $t_f/\delta t$ steps.
For each trajectory we count the number of quantum jumps, the jumps
corresponding to operator $a$ reduces the number of photons inside the
cavity and corresponds to a photon that leak the cavity. The jumps
corresponding to operator $\sigma_-$, send the atom back to the ground
state and corresponds to a spontaneous emission. The procedure to
register emissions in the two different channels is summarized in
algorithm. \ref{alg1}.

We realize a large number of these trajectories and keep track of the
numbers of emission for each channel, with this data we calculate
the joint probability distribution of the number of emissions in each
of the two channels.

@@

\begin{equation} \label{chaf1}
\expval{a}_{ss} = \frac{\mathcal{E}e^{-i\omega t} +
  g\expval{\sigma_-}_{ss}}{\kappa}\, ,
\end{equation}
\begin{equation} \label{chaf2}
\expval{\sigma_-}_{ss} = -\frac{2g}{\gamma}\frac{\expval{a}_{ss}}{1 +
  \frac{8g^2}{\gamma^2}|\expval{a}_{ss}|^2}\, ,
\end{equation}
\begin{equation}
\bigg(\frac{\mathcal{E}}{\kappa}\bigg)^2 = |\expval{a}_{ss}|^2 \bigg(1
+ \frac{2g^2}{\gamma \kappa}\frac{1}{1 +
  \frac{8g^2}{\gamma^2}|\expval{a}_{ss}|^2}\bigg)^2\, .
\end{equation}
When $\gamma \gg g$, the expected value of the number of photons inside
the cavity is 
\begin{equation} \label{numfo}
|\expval{a}_{ss}|^2 \approx \bigg(\frac{\mathcal{E}/\kappa}{1 + 2g^2/\gamma \kappa}\bigg)^2.
\end{equation}

\subsection{Quantum trajectories with fixed number of photons leaked from the cavity}
We calculate the distribution probability of the number of spontaneous
emission when a fixed number of photons leaked the cavity. We assume
that the mean number of photons inside the cavity is $1/9$. The
results are shown in Fig.~\ref{probdiss}. As the number of cavity
emissions increases, the mean number of spontaneous emissions
increases. This result is expected, because the number of cavity
emissions is correlated with the time we are counting spontaneous
emission from the atom: the larger the number of cavity
emissions the larger the time we count spontaneous emission,
which implies a larger mean number of emitted photons. Also, as shown
in Fig~\ref{graph}, the probability distribution is wider as the
number of leaked photons increases, this implies less accuracy
guessing the number of spontaneous emission. If we know the cavity
drive, this results does not imply that we can learn something extra
about the number of spontaneous emissions knowing the number of
photons leaked from the cavity; it is clear that when we increase the
time window where we count photons, both, the number of cavity emissions
and the number of spontaneous emissions, increases.

@@

\subsection{Quantum trajectories with fixed duration}
We consider the set of quantum trajectories of the same duration. This
corresponds to fixing the time we count photons. Each set of quantum
trajectories with the same duration is labeled with its mean number
of spontaneously emitted photons $\langle n_s\rangle$, given the system
parameters, a larger $\langle n_s\rangle$ implies quantum trajectories
with larger duration. We consider the case where we fix the mean
number of photons inside the cavity to $1$. As shown by
Eq.~(\ref{numfo}), this number depends on the drive, and cavity and
atomic parameters.

@@

Now we focus in the case, where given a set of quantum trajectories
with fixed duration $t_f$, we postselect all the trajectories where the
number of cavity emissions is a fixed number $n_c$, and plot
$p(n_s|n_c)$, the probability distribution of the number of spontaneous
emissions $n_s$, under the condition that $n_c$ cavity emissions
happened. If $p(n_s|n_c)\neq p(n_s)p(n_c)$, $n_s$ and $n_c$ are not
independent: information can be extracted about $n_s$ knowing $n_c$.
An example of this is shown in Fig.~\ref{probdisult}(a), where we
show $p(n_s|n_c)$, the probability distribution of $n_s$ postselected
to the case where the number of cavity emissions is
$n_c=\langle n_c \rangle$, and $n_c=\langle n_c \rangle\pm 3 \sigma$. We
see a positive correlation between the two random variables: the
maximum of the probability distribution increases (decreases) if we
postselect the trajectories with a larger than the mean (smaller than
the mean) number of cavity emissions. In Fig.~\ref{probdisult}(b), we
show that for a cavity with large $\kappa$, the change in the
probability distribution $p(n_s|n_c)$ is much smaller than in the case
for small $\kappa$. When
$\kappa\rightarrow\infty$, there are no correlation between the two
channels and $p(n_s|n_c)=p(n_s)p(n_c)$.
In the next section we calculate the correlation between $n_s$ and
$n_c$ for different $\kappa$.

@@

The results are shown in Fig. \ref{corrxy}. We observe a maximum
correlation, close to $0.1$, for $\kappa/\gamma\approx 0.05$. From
there the correlation decreases as $\kappa$ increases. The figure is
consistent with the statement that the correlation goes to zero as
$\kappa\rightarrow\infty$. With values for $\kappa/\gamma$ lower than
$0.05$, we notice that the correlations begins to decrease. The reason
is that, as the cavity linewidth decreases, the number of cavity
emissions decreases. In the limit where $\kappa=0$ the two random
variables becomes independent, because the output of $n_c$ is zero
with probability one. In this case there is no correlation between the
two random variables. Fig.~\ref{probdisult}(a), where the change in
$p(n_s|n_c)$ is larger, corresponds to a correlation around $0.1$;
Fig.~\ref{probdisult}(b), where the change is small, corresponds to a
correlation around $0.01$.

@@

\begin{acknowledgments}
This work was supported by DGAPA-UNAM under grant PAPIIT-IG120518.
\end{acknowledgments}
